\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{CJKutf8}

\begin{document}
\name{\Large Konrad Listwan-Ciesielski}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: [redacted]       \hfill LinkedIn: https://www.linkedin.com/in/klistwan \\
    \noindent Email: [redacted]  \hfill GitHub: https://github.com/klistwan \vspace{0mm}\\\vspace{-4.5mm}

    \section{\mysidestyle Professional\\Experience}

    \textbf{Cruise Automation}, San Francisco, US \vspace{1mm}\\\vspace{1mm}%
    \textsl{Senior Software Engineer} \hfill \textbf{2017 -- 2019}\\
    Infrastructure and back-end software development at a self-driving car company, with a focus on data ingestion software between Cruise's fleet of cars and on-premise applications. Work included:

    \begin{itemize}
    \item Designed and built a highly-scalable service to copy 150 TB of data per day from on-premise storage to Google Cloud Storage in Python
    \item Created a mid-term data ingestion strategy to support a fleet of 300+ vehicles producing 500 TB of data per day (reviewed and approved by the SVP of Engineering)
    \item Developed a data preservation request in C++ to prevent data loss during airbag deployment
    \item Migrated existing data infrastructure services from GlusterFS to OpenStack Swift
    \item Interviewed 200+ candidates for domain knowledge, coding skills, and architecture design for senior engineering and engineering manager positions
    \end{itemize}
    \vspace{-4mm}
    \textbf{Kira Talent}, Toronto, Canada \vspace{1mm}\\\vspace{1mm}%
    \textsl{Co-Founder, CTO} \hfill \textbf{2012 -- 2016}\\
    Build an asynchronous video interviewing system using Python, Django, MySQL, JavaScript that resulted in the first \$10,000 in revenue and \$300,000 in angel financing. Hired and led a team of 8 to execute on roadmap, growing the company to \$2M in annual recurring revenue and \$8M in venture financing. Established engineering best practices (e.g. code reviews, sprint retrospectives, bug triage, continuous integration, etc) to improve product quality and developer happiness. Integrated usability studies, research and market analysis into product requirements, leading to 99\% client retention

    \textbf{Minted}, San Francisco, US \vspace{1mm}\\\vspace{1mm}%
    \textsl{Software Engineering Intern} \hfill \textbf{Winter 2012}\\
     Built features using Python (Bottle, Mako), JavaScript (jQuery, Backbone.js), PHP and MySQL to help re-launch the Minted Wedding Suite. Wrote hundreds of unit tests to increase test coverage across many aspects of the codebase, in JavaScript (JUnit) and Python (Nose).
     
    \textbf{Nuance}, Montreal, Canada \vspace{1mm}\\\vspace{1mm}%
    \textsl{Data Science Intern} \hfill \textbf{Summer 2011}\\
    Data mined large data sets using R and created visualizations using ggplot2 for the Data Team to improve the tagging speed and cluster rates of a semantic clustering algorithm. Built tools to extract and transform network speech data. Created a system to predict success rates of automatic number identification systems across verticals and fallback methods

    \section{\mysidestyle Education}

    \textbf{\begin{CJK}{UTF8}{min}ISI日本語学校\end{CJK}}, Tokyo, Japan \vspace{1mm}\\\vspace{1mm}%
    \textsl{Advanced Japanese Studies} \hfill \textbf{2019 -- Present}\\
    Coursework in reading, writing, listening, speaking. Successfully passed JLPT N2.

    \textbf{Thompson Rivers University}, Online \vspace{1mm}\\\vspace{1mm}%
    \textsl{Bachelor of Computing Science} \hfill \textbf{2017 -- Present}\\
    Received A+ in many courses: operating systems, computer networks, object-oriented programming \& design, embedded \& robotic programming, and algorithm design \& analysis. Built an autonomous path-finding robot to navigate a maze using an Arduino and a distance sensor.

    \textbf{University of Waterloo}, Waterloo, Canada \vspace{1mm}\\\vspace{1mm}%
    \textsl{Bachelor of Math in Computer Science} \hfill \textbf{2010 -- 2012}\\
    Awarded President’s Scholarship of Distinction (95\%+ average) upon entrance. Took leave of absence to start Kira Talent.

\end{resume}
\end{document}